\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{microtype} % Improves typesetting and helps with justification warnings

% Personal data
\name{Marcos}{Mayorga}
\email{mm@mm-studios.com}
\phone[mobile]{+44 07986800521}
\address{London, UK}
\social[linkedin]{linkedin.com/in/marcosmayorga}

\begin{document}
\makecvtitle

\section{Summary}
\cvitem{}{\small 8 years experience leading roles Head of Engineering/CTO in blockchain startups, running dev teams in cooperation with C-suite roles.}
\cvitem{}{\small Multidisciplinary developer/lead with over 20 years writing software across different industries finance, blockchain, supercomputing, aerospace, and distributed networks. Strong scientific foundation, with deep expertise in modern C++ (17/20/23), multithreading, real-time debugging, and simulation. Proven track record building mission-critical software in HPC environments, trading systems, and P2P infrastructure. Goal-oriented, team-driven, and focused on solving complex engineering challenges with precision and rigor.}

\section{Core Skills}
\cvlistdoubleitem{Modern C++ (17/20/23)}{debian GNU/Linux}
\cvlistdoubleitem{STL, multithreading}{low-latency systems}
\cvlistdoubleitem{Distributed Systems}{Architecture}
\cvlistdoubleitem{OOP, TDD}{Design patterns}
\cvlistdoubleitem{Trading systems}{Embedded systems}
\cvlistdoubleitem{Airborne safety-critical}{P2P Networks}
\cvlistdoubleitem{CD/CI, GNU/Linux}{Fast time simulation}
\cvlistdoubleitem{Debugging, profiling, optimization}{compiler tooling}
\cvitem{1st Langs}{C++, java, bash}
\cvitem{2nd langs}{Rust, go, javascript, python and web langs.}
\cvitem{Interest}{AGI/AI, Science, Technology, Innovation, Entrepreneurship}
\cvitem{Research}{Blockchain and privacy wallets with role based agents and AI/LLM in distributed networks}

\section{Education}
\cvitem{1998}{Graduated M.Sc. Physics. Solid State Physics. Universidad Autonoma de Madrid (Spain)}

\section{Experience}
\cventry{Feb 2024 -- Jun 2025}{CTO}{Script Network}{London}{}{
\begin{itemize}
    \item Run high performance dev team enforcing discipline and routines.
    \item Developed decentralized video streaming system with 2 L1 blockchain. Fork based on Theta (Go) + scriptv (C++).
    \item Implemented business cryptoeconomics in PoS system.
    \item Colaborated with Node reseller partners.
    \item Mentored team and created the Script Network developer community.
    \item Implemented automated deployment pipeline on cloud.
    \item Responsible for weekly stage and production deployments on AWS and gcloud.
    \item \textbf{Languages:} C++, Bash, golang, javascript, java
    \item \textbf{Tools:} Debian GNU/Linux, Git, systemd, nginx, mongoDB, redix, postgreSQL
\end{itemize}}

\cventry{April 2019 -- Present}{Founder CTO}{KATLAS Technology}{London, UK}{}{
\begin{itemize}
    \item Co-founder of blockchain start-up focused on privacy-respecting distributed systems.
    \item Tech partner providing consultancy and implementation task force for digital transformation.
    \item Delivered MVP for the Health Industry integrating AI devices on a P2P platform.
    \item Built the Plebble P2P crypto platform and healthcare product MaiHealth.
    \item Maintainer of curated codebase with 120,000 lines of code.
    \item \textbf{Languages:} C++, Bash
    \item \textbf{Tools:} Bash, Debian GNU/Linux, Docker, Git, tmux
\end{itemize}}

\cventry{Jan 2021 -- Jul 2021}{Protocol Engineer}{NEM - New Economic Movement}{London, UK}{}{
\begin{itemize}
    \item Built wallet-CLI SDK in C++ for Symbol blockchain.
    \item Develped wallet interface to hardware wallets: Ledger, Trezor.
    \item Researched distributed storage.
    \item Helped integration with partners and exchanges under launch pressure.
    \item Implemented consensus components and P2P protocol logic.
    \item Received XYM token reward for performance during launch phase.
    \item \textbf{Languages:} C++
    \item \textbf{Tools:} confluence
\end{itemize}}

\cventry{Apr 2019 -- Present}{Co-founder / CTO}{KATLAS Technology}{London}{}{
\begin{itemize}
    \item Secure enclaves using Morello CHERI architecture.
    \item Development of platform and DEMOS of ecosystems with role-based agents.
    \item Web3 Router. A design of a internet router integrating blockchain node and smart privacy wallets.
    \item \textbf{Languages:} C++, Bash
    \item \textbf{Tools:} debian Linux, git, FreeBSD, clang
\end{itemize}}

\cventry{Apr 2018 -- Apr 2019}{Head of Engineering}{Atlas City Finance}{London, UK}{}{
\begin{itemize}
    \item Led a team of 9 engineers in the design and implementation of a novel experimental cryptocurrency platform.
    \item Architected a resilient, consensus-based full-node operating system built on Debian GNU/Linux.
    \item Designed the cryptographic wallet and peer-to-peer protocols for the system.
    \item Mentored developers and coordinated cross-functional technical decisions.
    \item \textbf{Languages:} C++, Bash
    \item \textbf{Tools:} Debian GNU/Linux, GitLab
\end{itemize}}

\cventry{Nov 2017 -- Apr 2018}{Senior Research Engineer}{nChain}{London}{}{
\begin{itemize}
    \item Served as a Bitcoin Cash researcher and C++ backend developer at a blockchain startup, with a focus on scalable untrusted P2P systems.
    \item Produced Proof-of-Concept implementations for disruptive cryptographic and consensus mechanisms.
    \item Authored technical white papers on experimental cryptocurrency designs and innovations.
    \item Acted as main developer in the Bitcoin ABC task force; contributed 9 new opcodes for the May 2018 'Monolith' hard fork.
    \item Developed 'swissknife', a standalone C++ utility for blockchain researchers.
    \item Supported R\&D efforts in smart contracts, zero-knowledge privacy, and verifiable computation.
    \item Proposed and implemented new Bitcoin Script opcodes such as OP\_RAND and OP\_CHECKCOMP.
    \item \textbf{Languages:} C++
    \item \textbf{Tools:} Debian GNU/Linux, CMake, Git, LaTex
\end{itemize}}

\cventry{Nov 2017 -- April 2018}{Lead developer}{nChain}{London}{}{
\begin{itemize}
    \item Led the initial design and development of the Nakasendo SDK, nChain's Blockchain SDK.
    \item Published the research paper 'Computing Non-Primitive Recursive Functions Using a Total Turing Language'.
    \item Proposed and implemented extensions to Bitcoin-core scripting language with loop-related opcodes.
    \item Developed a step-by-step debugger for Bitcoin Script.
    \item Designed and implemented HLLC, a high-level language compiler targeting Bitcoin Script.
    \item Created a protocol for fiat currency transfer via encoded Bitcoin transactions.
    \item Researched and prototyped zk-SNARK circuits.
    \item \textbf{Languages:} C++
    \item \textbf{Tools:} Debian GNU/Linux, Git, Bitcoin codebase
\end{itemize}}

\cventry{Jun 2016 -- Feb 2017}{Senior Developer}{ARM (Allinea)}{Warwick}{}{
\begin{itemize}
    \item Senior developer at a leading company in the High-Performance Computing (HPC) industry.
    \item Maintained and enhanced the codebase of a flagship parallel debugging suite.
    \item Optimized highly parallel scientific models on Cray and IBM Blue Gene platforms.
    \item Handled advanced L2 technical support cases.
    \item Co-Authored technical proposals for submission to the C++ Standardization Committee.
    \item \textbf{Languages/libs:} C++, CUDA, Qt
    \item \textbf{Tools:} Debian GNU/Linux, gdb, MPI, valgrind, slurm, JIRA, hg (mercurial), jenkins
\end{itemize}}

\cventry{Nov 2015 -- May 2016}{Senior Software Engineer}{Airbus Defence \& Space}{Stevenage, London, UK}{}{
\begin{itemize}
    \item Simulation Engineer (contractor) in the Functional Verification division for space systems.
    \item Developed automated test procedures for flight hardware (reaction wheels) for the Solar Orbiter mission.
    \item Developed automated test procedures for electrical subsystems for the Mars Rover.
    \item \textbf{Languages:} C++, Java
    \item \textbf{Tools:} g++, gdb, eclipse
\end{itemize}}

\cventry{Aug 2011 -- Nov 2015}{Founder / CTO}{FairLuck}{Madrid}{}{
\begin{itemize}
    \item Founded and led an experimental venture exploring provably fair online gaming.
    \item Designed and implemented a real-time multiplayer game server in C++.
    \item Developed custom secure RNG and deterministic game state validation tools.
    \item Presented technology to regulatory bodies including UK Gambling Commission.
    \item Designed and implemented an investment product leveraging sportsbook betting markets.
    \item Designed and implemented a Currency Exchange (Curex/trocavaluta).
    \item \textbf{Languages:} C++, HTML, CSS, javascript
    \item \textbf{Tools:} CMake, Debian GNU/Linux, svn, postgreSQL
\end{itemize}}

\cventry{Sep 2006 -- Jun 2011}{Staff Senior Software Engineer (E4)}{Boeing Research \& Technology Europe}{Madrid}{}{
\begin{itemize}
    \item Airspace Simulation Software Architect and Technical Team Leader.
    \item Introduced open-source development practices.
    \item Delivered DEMO in Seattle on decentralized collision avoidance systems for flying cars.
    \item Managed external collaboration with two technology firms and one university.
    \item Implemented an aircraft-to-aircraft intent negotiation protocol.
    \item \textbf{Languages/libs:} C/C++, XML, UML, boost, gtk+, WxWindows
    \item \textbf{Tools:} CMake, Debian GNU/Linux, svn, matlab, x-plane
\end{itemize}}

\cventry{Dec 2005 -- Sep 2006}{Simulation Engineer}{GMV / GIMO (Spanish Navy Research Facility)}{Madrid}{}{
\begin{itemize}
    \item NATO Clearance.
    \item Designed and implemented a continuous-time simulator for a NATO project (naval warfare/chaff/missile guidance).
    \item Developed a XML dialect to generate C++ code snippets.
    \item \textbf{Languages/libs:} C++, XML, OSG
    \item \textbf{Tools:} Debian GNU/Linux, GNU Plot, open office XML, autotool
\end{itemize}}

\cventry{Sep 2004 -- Dec 2005}{Real-time Safety critical Software Engineer}{Silver Software - EADS - CASA}{Madrid, ES}{}{
\begin{itemize}
    \item Developed military Air Refueling Boom System (guidance/control) for A330 MRTT aircraft.
    \item Implemented DO-178 safety protocols and synchronized fault-tolerant subsystems.
    \item Main analyst and developer of the 4x redundant control system under CMMI-5, SIL-4 regulations.
    \item Managed system requirements and maintained full test coverage.
    \item \textbf{Languages:} C++, Ada, Spark, UML
    \item \textbf{Tools:} VxWorks, gnats, doors, bugzilla, CVS, Rational RTRT
\end{itemize}}

\cventry{Jun 2004 -- Sep 2004}{Real-time Software Engineer}{Silver Software}{Chippenham, UK}{}{
\begin{itemize}
    \item Westinghouse: Development of a real-time/signaling subsystem for the Westlock Rail system.
    \item Worked on IMA (Integrated Modular Avionics) for A380 landing gear.
    \item \textbf{Languages:} C++
    \item \textbf{Tools:} Visual C++, MFC, python
\end{itemize}}

\cventry{Oct 2003 -- June 2004}{Software Engineer}{Rastertech}{Madrid}{}{
\begin{itemize}
    \item Worked on the main product, a workflow tool for engineering blueprints.
    \item \textbf{Languages:} C++
    \item \textbf{Tools:} Visual C++, knoppix, AutoCAD, Catia, Pro-Engineer
\end{itemize}}

\cventry{May 2003 -- Oct 2003}{Software Engineer}{Helgeson Scientific}{Madrid}{}{
\begin{itemize}
    \item Development of capture and analysis Software on alpha particle detector for nuclear reactor contingencies.
    \item \textbf{Languages:} C++
    \item \textbf{Tools:} Borland C++
\end{itemize}}

\cventry{Oct 2000 -- Apr 2003}{Software Engineer}{ELCO-Tecnobit}{Madrid}{}{
\begin{itemize}
    \item Developed bespoke CAD software for Human-Machine Interfaces (HMI) for the Airbus A400M.
    \item Main developer for embedded avionics on military helicopters (Seaking, Seahawk).
    \item Implemented geophysical models (WMM, EGM96) and integrated global cartographic systems.
    \item \textbf{Languages:} C++, Java, OpenGL
    \item \textbf{Tools:} Debian GNU/Linux, Netbeans, Visual C++, DirectX
\end{itemize}}

\cventry{Oct 1998 -- Oct 2000}{Web Developer/founder of .com startup}{IP Iberproject}{Madrid}{}{
\begin{itemize}
    \item Development of irccrawler.com, e-commerce websites for advertisements on IRC networks.
    \item Proposed and awarded a project for Telefónica I+D backend systems.
    \item Developed promotional microsite for Coca-Cola.
    \item \textbf{Languages:} PHP, SQL, ASP, Visual Basic, Excel VBA, perl
    \item \textbf{Tools:} Debian GNU/Linux, Apache, MS SQL Server, Director/flash
\end{itemize}}

\cventry{Dec 1997 -- Oct 1998}{Software developer}{Solucion PYME}{Madrid}{}{
\begin{itemize}
    \item Development of business applications in the retail industry.
    \item Grew and lead the development team.
    \item \textbf{Languages/libs:} Visual Basic, ASP, ActiveX, ODBC, OLAP
    \item \textbf{Tools:} MS Access, MS SQL Server, IIS
\end{itemize}}

\cventry{Sep 1996 -- Nov 1996}{Programmer}{A.R. Software}{Madrid}{}{
\begin{itemize}
    \item Developed IBM7525 protocol handler and legacy terminal emulation tools.
    \item \textbf{Languages:} C, x86 Assembly
    \item \textbf{Tools:} Borland C, RS232 interface
\end{itemize}}

\section{Publications}
\cventry{2023}{Plebble: Blockchain, Local Economies, Marketplaces and Social Order}{}{}{}{\href{http://plebble.net/plebble_white_paper.pdf}{http://plebble.net/plebble\_white\_paper.pdf} \\ White paper describing Plebble Layer 1 blockchain.}
\cventry{2017}{Computing Non-Primitive Recursive Functions Using a Total Turing Language}{}{}{}{\href{http://plebble.net/ackermann_bitcoin.pdf}{http://plebble.net/ackermann\_bitcoin.pdf} \\ Proof that Bitcoin Script can compute non-primitive recursive functions.}

\section{Demos}
\cventry{2023}{Patient Journey Demo (Plebble)}{}{}{}{\href{http://plebble.net/patient_journey.pdf}{http://plebble.net/patient\_journey.pdf} \\ Role-based agent systems in healthcare.}
\cventry{2025}{Supply Chain Demo (Plebble)}{}{}{}{\href{http://plebble.net/supply_chain__demo.pdf}{http://plebble.net/supply\_chain\_\_demo.pdf} \\ Blockchain traceability system.}

\section{Source Code}
\cvitem{mm-s}{\href{https://github.com/mm-s}{https://github.com/mm-s} -- Project sandbox and essays}
\cvitem{Plebble}{\href{https://github.com/root1m3/plebble}{https://github.com/root1m3/plebble} -- P2P network, privacy wallets, agent orchestration}
\cvitem{ScriptV}{\href{https://github.com/scriptnetwork/scriptv}{https://github.com/scriptnetwork/scriptv} -- Script.tv Layer-1 node codebase}
\cvitem{dTool}{\href{https://github.com/scriptnetwork/dtool}{https://github.com/scriptnetwork/dtool} -- DevOps/CI and dev discipline team automation tool.}

\section{Major Open Source Contributions}
\cventry{2018}{Bitcoin ABC}{}{}{}{
Contributed extensively to the May 2018 Monolith protocol upgrade by implementing and testing new Bitcoin Script opcodes.
\begin{itemize}
    \item Implemented arithmetic/bitwise opcodes: OP\_DIV, OP\_MOD, OP\_AND, OP\_OR, OP\_XOR.
    \item Developed string manipulation opcodes: OP\_CAT, OP\_SPLIT, OP\_NUM2BIN, OP\_BIN2NUM.
    \item Submitted and reviewed over 20 Differential Revisions and Commits.
    \item \href{https://reviews.bitcoinabc.org/search/query/BkuPPBzbERC3/\#R}{Link to contributions}
\end{itemize}}

\section{Languages}
\cvitem{Spanish}{Native}
\cvitem{English}{Fluent}

\section{Other}
\cvitem{2006}{Security Clearance. Previously NATO cleared (GMV/GIMO Naval Research)}
\cvitem{1997}{Served mandatory military service for Spanish Army}

\end{document}
